\chapter{Conclusion}

The purpose of this project was to make a system, which integrates different technologies. In the process of developing this system, the design went through a lot of phases, each making the system more flexible and scalable. Even though scalability is not a focus point of this project, making the system scalable has helped making different "moving parts" interchangeable, thereby making integration with other systems possible in the future.  

New technologies have been researched, mainly RabbitMQ and RSA encryption. RabbitMQ is what makes the servers scalable through copying, and it also opens up doors for further integration of systems with and by ChatX. A lot of work has gone into the RSA encryption, and encryption in general, but because so much time went with designing and redesigning the system, the encryption was never implemented. 

%ChatX have been a very design heavy system where a lot of thoughts went into how the system should be designed.

\section{Future Work}

There was a larger amount of features which did not get implemented due to the scale of the project, but it is possible to extend the system with these features in the future with minimal changes and additions to the current system.

One possible addition to the system would be another client, e.g. a web client. This has not been a high priority, as the current solution requires a socket connection which is difficult to implement in standard HTML. Furthermore, the integration of the used technologies proved to be more difficult and time consuming than anticipated. Lastly, SSL would need to be implemented to make the solution secure and encrypted.
 
Voice over IP(VoIP) and video chat was another technology that was considered to be implemented. A few changes could make this possible on the current clients, but for a web client either a plugin and/or a cloud service would be necessary. 

A thought was also at the client side to be able to embed e.g. instance media, such as videos and images directly into the chat and make it possible to view without opening external tools or programs.

Lastly an idea was to make a multi platform encryption system. Such a system could have simplified some of the work, as some systems does not communicate well with each other, but making such system fell out of scope of the course.
